Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-25 02_Paper/paper.tex
correcting typos

The quality control of production processes and products is one part of the general quality management
and contains the measures and activities needed to fulfill the quality requirements \cite{illes2017new}.
According to Illés, currently there are three established tools and methods of quality control \cite{illes2017new}:
The Statistical Process Control (SPC), Auditing, and Total Quality Control (TQC).   
The SPC is used to monitor the production process using recorded data values for the quality characteristics and to indicate any significant changes
in the quality characteristics in the production process \cite{selvamuthu2018introduction}. It can take place before and after a manufacturing process
as off-line SPC or implemented in the manufacturing process as in-line SPC.
With SPC, large batches can be checked, but it is only possible, if the variance of the process parameters and product quality is small enough,
to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
Auditing, in this case especially product and process auditing, is the most fundamental quality control technique. 
Product and process auditing is the independent examination of product and process quality to provide information. This is executed by
an independent auditor, based on sampling, or checking records. But the auditor is just reporting incorrect processes or products. The required adapting is done by others \cite{fox1993quality}.
Both statistical methods and hundred percent controls can be applied as an audit tool.
Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and hundert percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
In the case of a hundred percent control, this is associated with higher costs and higher requirement of time compared to a quality control based on a machine learning model.
Statistical methods are faster but have the same problem like the SPC: This methods are prone to errors, if the variance of the product quality is to high.
The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
by involving all departments of the organization \cite{illes2017new}.
The quality characteristics of a product can be classified as variables or attributes.
Variables are measurable characteristics, which are shown as numbers. On the contrary,
attributes are not measureable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, 
precise measured values are available, which enable precise adjustment of the process parameters. 
This allows the desired quality to be restored. With that in mind, a predictive quality control is a promising solution.

>>>>

The quality control of production processes and products is one part of the general quality management
and contains the measures and activities needed to fulfill the quality requirements \cite{illes2017new}.
According to Illés, currently there are three established tools and methods of quality control \cite{illes2017new}:
The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC).   
The SPC is used to monitor the production process using recorded data values for the quality characteristics and to indicate any significant changes
in the quality characteristics in the production process \cite{selvamuthu2018introduction}. It can take place before and after a manufacturing process
as off-line SPC or implemented in the manufacturing process as in-line SPC.
With SPC, large batches can be checked, but it is only possible, if the variance of the process and product parameters is small enough,
to ensure process capability \cite{kahle2013zuverlaessigkeitsanalyse}.
Auditing, in this case especially product and process auditing, is the most fundamental quality control technique. 
Product and process auditing is the independent examination of product and process quality to provide information. This is executed by
an independent auditor, based on sampling, or checking records. But the auditor is just reporting incorrect processes or products. The required adapting is done by others \cite{fox1993quality}.
Both statistical methods and hundred percent controls can be applied as an audit tool.
Statistical methods such as acceptance sampling or quality control charts represent a compromise between zero and hundred percent control \cite{selvamuthu2018introduction, kurniati2015quality}.
In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
Statistical methods are faster as hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
if the variance of the product quality is to high.
The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
by involving all departments of the organization \cite{illes2017new}.
The quality characteristics of a product can be classified as variables or attributes.
Variables are measurable characteristics, which are shown as numbers. On the contrary,
attributes are not measureable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, 
precise measured values are available, which enable precise adjustment of the process parameters. 
This allows the desired quality to be restored. With that in mind, a predictive quality control is a promising solution.
